TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-10-12 paper/draft.tex
improve captions

%---------------------------
\begin{figure}[ht]
\plotone{figures/aspcap_cannon_validation.png}
\caption{Validation test of \cannon\ temperatures (left), as compared to \aspcap\ temperatures (right) using three different color-temperature relations derived from \citealt{Mann:2015}, \citealt{Casagrande:2008}, and \citealt{Boyajian:2013}. We find \cannon\ temperatures to be significantly more consistent with all three relations in terms of bias and scatter. \label{fig:aspcap_cannon_validation}}
\end{figure}

@@

\begin{figure}[ht]
\plotone{figures/mann_radii.png}
\caption{Comparison of radii estimated from M15 relations. \label{fig:radii}}
\end{figure}

>>>>

%---------------------------
\begin{figure}[ht]
\plotone{figures/aspcap_cannon_validation.png}
\caption{\cannon\ (right column) and \aspcap\ (left column) temperatures as compared to temperatures estimated from visible and infrared color-temperature relations from three different literature sources for a subsample of 6,000 sources. Shown are \cannon\ and \aspcap\ temperatures (x-axis) compared to temperatures estimated from the \citealt{Mann:2015} $V-J$ and [Fe/H] dependent relation (top), \citealt{Casagrande:2008} $V-K$ relation (middle), and the \citealt{Boyajian:2013} relation (bottom). We find \aspcap\ overestimates \teff\ on average by about 130K for the M15 and B13 relations about 220K for the C08. Additionally we see the scatter much higher for the \aspcap\ temperatures ($\sim220$K) compared to the scatter of \cannon\ temperatures ($\sim80-100$K), the scatter for both \aspcap\ and \cannon\ temperatures largely due to variation in metallicity.  \label{fig:teff_comparisons}}
\end{figure}

@@

\begin{figure}[ht]
\plotone{figures/mann_radii.png}
\caption{Comparison of radii estimated from M15 relations: on the x-axis radii are derived from  K magnitudes and \cannon\ [Fe/H], on the y-axis radii are derived from \cannon\ \teff\ and [Fe/H]. \label{fig:radii}}
\end{figure}
